Title

### 2023-04-16 main.tex
Algunos cambios

% Use "Eq" instead of "Equation" for equation citations.
% }}}
\section*{Introduction} % {{{
%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.%~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\begin{eqnarray}
\label{eq:schemeP}
	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
\end{eqnarray}
% }}}
\section{Circuits for Pauli Maps}  \label{sec: Circuits for Pauli Maps} % {{{
% Intro  {{{
\textbf{Lista de puntos:}
\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
\end{itemize}

In this section \cpnote{ser coherente con las subsecciones que se tienen nota que no 
hay mencion a los quantum channels. Menos
cuadrado, quizá pasar por chatgpt. hacerlo al final cuanod se tenga el capitulo
por lo menos leido y aprobado en principio de mi parte.} we introduce the
concept of Pauli channels and Pauli dynamical
maps, as well as proposal for a quantum circuit that simulates them on systems
of $N$ qubits.  Furthermore, we show the results of implementing the circuit on
a quantum computer for the particular case of Pauli channels of one qubit. 
% }}}
\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{

@@

Quantum channels are the most general linear operations that a 
quantum system (which is represented by a density matrix $\rho$) 
can undergo independently of its past~\cite{zimansbook,cirac}. 
These channels are constructed based on three fundamental properties: 
linearity, trace preservation, and complete positivity.

Linearity ensures that a quantum channel $\mathcal{E}$ maps any convex
combination of density matrices into a convex combination of their evolution.
The trace preserving property is given by $\tr \mathcal{E}[\rho] = \tr \rho =
1$ and guarantees that the quantum channel occurs with a probability of $1$.
The complete positivity condition ensures that the quantum channel preserves
positive semidefiniteness.  A linear map $\mathcal{E}$ is considered positive
if it maps density operators to density operators ($\mathcal{E}(\rho) \geq 0$
for all density matrices $\rho$).  If the extension of a positive map to
include an ancilla results in another positive map, the original map is said to
be completely positive~\cite{geometry}.  This property is required for quantum
channels to allow for the proper evolution of potentially entangled states with
an ancilla.

Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm to test
for complete positivity of a quantum channel.  The algorithm exploits the
isomorphism between a channel $\mathcal{E}$ and the state $\mathcal{D} =
(\text{id} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, where
$|\Omega\rangle$ is a maximally entangled state between the original system and
an ancilla and “id” is the identity channel.  Remarkably, the map $\mathcal{E}$
is completely positive if and only if $\mathcal{D}$ (also known as the Choi or
dynamical matrix of $\mathcal{E}$) is positive semidefinite.

@@

To define a Pauli channel, we start by exploring the single-qubit scenario and
then the $N$-qubit one.  First of all, the most general single-qubit density
matrix can be written as
\begin{eqnarray}
\label{ec: Density Matrix}
\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
\end{eqnarray}
with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
Normalization requires that $r_0 = 1$ and the remaining $r_{1,2,3}$ form a
Bloch vector \cpnote{explicar un poco mejor. Me parece que para el publico vale 
la pena ser un poco mas explicito. pero no estoy muy seguro. }. 
A Pauli channel is defined as an operation
that applies a convex combination of Pauli matrices to the density matrix in the following way:
\begin{eqnarray}
\label{ec: Pauli channel 1 qbit}
\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
\end{eqnarray}
where $k_{\gamma}$ are non-negative real numbers such that 
$\sum_{\gamma} k_{\gamma} = 1$ (these conditions are needed for the channel 
to be completely positive and trace preserving). 
\cpnote{en todo hay que mejorar un poco la redaccion. Aca me gustaria que 
se interpretara. Creo qe es mas que atenuacion de los componentes, o es solo atenuacion? 
en todo caso ver mejor como va la cosa. }

Having defined the one qubit case, 
in order to present the $N-$qubit one, we 
need to introduce the so-called \textit{Pauli strings}, defined as
\begin{eqnarray}
\label{ec: Pauli string}
\sigma_{\vec{\alpha}} = \sigma_{\alpha_1} \otimes \sigma_{\alpha_2}\otimes \cdots \otimes \sigma_{\alpha_N},
\end{eqnarray}
where $\vec{\alpha}$ denotes a multi-index $(\alpha_1, \cdots, \alpha_N)$
 and $\alpha_i \in \{0,1,2,3\}$. 
 These operators form an orthogonal basis in the space of operators acting on $N$ qubits. 
 Similarly to the single-qubit case, the density matrix $\rho$ 
of a system of $N$ qubits can be written using Pauli strings as:
\begin{eqnarray}
\label{ec:  Density matrix Nqbit}
\rho = \dfrac{1}{2^N} \sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
\end{eqnarray}
Then, we define a Pauli channel as a transformation of the density 
matrix given by
\begin{eqnarray}
\label{ec: pauli channel N-qubt}
\mathcal{E}(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}} \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
where just as before, complete positivity and trace preservation requires
that $k_{\vec{\gamma}}$ are positive real numbers such 
that $\sum_{\vec{\gamma}} k_{\vec{\gamma}}=1$.

\cpnote{Creo qeu toca motivar, conectar con cosas conocidas y en general no ser tan seco}
% }}}
\subsection*{Circuit for a Pauli Channel} % {{{
\label{subsec: Circuit for a Pauli Channel}

@@

We are interested in constructing a quantum circuit that can implement an
arbitrary Pauli channel on a system of $N$ qubits. 
To do it, it is important to realize that a Pauli channel
 as shown in Eq~(\ref{ec: pauli channel N-qubt})  can 
be interpreted as a transformation that applies
each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.

Given this interpretation of the channel, 
it is easy to construct a quantum circuit that implements 
it with the help of $2n$ ancilla qubits.
The circuit that does this is presented in Fig~(\ref{fig: circuit-pauli}) and its 
first step in the circuit is to create the state
\begin{eqnarray}
\label{ec: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ is in general a complex number such that 
\begin{eqnarray}
\label{ec: b}
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.
\end{eqnarray}
Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
\begin{eqnarray}
|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
\end{eqnarray}
where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\

@@

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1} }} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS. Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel 
on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on $2N$ ancilla qubits and then uses them to apply
all possible Pauli strings on the principal qubits
with probabilities $k_{\vec{\gamma}}$.}
\label{fig: circuit-pauli}
\end{figure}

@@

\subsubsection*{Simulation for one-qubit Pauli channels} % {{{
\label{subsec: Simulation for one-qubit Pauli channels}
For the particular case of a Pauli channel on one qubit, 
the circuit that simulates it can be constructed as in Fig~(\ref{fig: citcuit-pauli-1}),
 which is a special case of Fig(\ref{fig: circuit-pauli}).

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$aq_1$} & \gateinput{$b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{\tbnote{Al igual que antes, hay que adaptar esta figura y quitarla antes de entregar}. {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
\label{fig: citcuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available,
we sampled $250$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, the accuracy of the implementation in the quantum computer
was quantified by calculating the
 process fidelity of the Choi matrix obtained by performing
quantum process tomography to the circuit
with respect to the theoretical Choi matrix of
the corresponding channel.
Finally, using the well known fact that one-qubit Pauli channels can be represented
as points in a tetrahedron with corners $(1,1,1), (1-1,-1), (-1,1,-1)$ and $(-1,-1,1)$, 
in Fig~(\ref{fig: fidelity one qubit}).
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{fidelity-points.png}\\
\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}. {\bf Fidelities one-qubit Pauli channel} Fidelities of one-qubit Pauli channels implemented on IBM's ibmq-lima. The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the fidelity of each channel's implementation using the circuit for a 1-qubit Pauli channel}
\label{fig: fidelity one qubit}
\end{figure}
% }}}
\subsubsection*{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

>>>>

% Use "Eq" instead of "Equation" for equation citations.
% }}}
\section*{Introduction} % {{{

% }}}
\section{Pauli Channels}  \label{sec: Pauli Channels} % {{{
% Intro  {{{
\textbf{Lista de puntos:}
\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
\end{itemize}

In this section \cpnote{ser coherente con las subsecciones que se tienen nota que no 
hay mencion a los quantum channels. Menos
cuadrado, quizá pasar por chatgpt. hacerlo al final cuanod se tenga el capitulo
por lo menos leido y aprobado en principio de mi parte.} we introduce the
concept of quantum channels, focusing on a specific type called Pauli channels.
Finally, we consider Pauli dynamical maps, which
are curves of Pauli channels parametrized by a variable.

%Quitarrrr:
Then, we propose a quantum circuit that simulates N-qubit Pauli channels
and show the results of implementing the circuit for $N=1$ on
a quantum computer. 
% }}}
\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{

@@

In quantum mechanics, a closed system is represented by a state vector in a 
Hilbert space $\mathcal{H}$. 
The state's evolution is given by Schrodinger's
equation and is always unitary.
However, in real-world situations, 
quantum systems are usually open and interact with their environment in various complicated ways. 
For example, the system's state may become entangled with the environment,
which can lead to loss of information of the system's state over time.

Instead of vectors in the Hilbert space $\mathcal{H}$,
open systems are described by matrices $\rho$ acting on $\mathcal{H}$
called density matrices and they include information about 
the system's interaction with the environment.
To be physically valid, a density matrix $\rho$
has to satisfy the two following conditions:
1. $\tr(\rho) =1$ and 2. $\rho$ is positive semi-definite $(\rho \geq 0)$.

Given that, we can finally define quantum channels, which
describe the time evolution of open quantum systems.
Quantum channels are the most general linear operations
that a quantum system (which is represented 
by a density matrix $\rho$) can undergo independently of its
past~\cite{zimansbook,cirac}.
These channels are constructed based on three fundamental properties: 
linearity, trace preservation, and complete positivity.

Linearity ensures that a quantum channel $\mathcal{E}$ maps any ensemble
of density matrices into the corresponding ensemble of their evolution.
The trace preserving property is given by $\tr (\mathcal{E}[\rho]) = \tr (\rho) =
1$ and guarantees that the quantum channel does not change the condition that $\tr(\rho) = 1$.
Finally, the channel should also preserve
the condition $\rho \geq 0$, and a map that does this is called a positive map.
However, positivity of $\mathcal{E}$ is not enough, 
and we actually require the more restrictive condition of complete positivity.
Complete positivity means that
$\mathcal{E} \otimes \mathbb{I}_n$ is positive for
any positive integer $n$ 
(where $\mathbb{I}_n$ is the $n\times n$ identity matrix).
This is required to ensure that even if $\rho$ is entangled with another system,
applying $\mathcal{E}$ to $\rho$ while doing nothing to the
 other system still results in  a positive semidefinite state.

Given a possible quantum channel $\mathcal{E}$, 
the condition of trace preservation is straightforward to examine but complete positivity is not as simple.
To test complete positivity of a quantum channel, 
Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm.  
The algorithm exploits the
isomorphism between a channel $\mathcal{E}$ and the state $\mathcal{D} =
(\mathbb{I} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, where
$|\Omega\rangle = 1/\text{dim}(\mathcal{H}) \sum_{i}^{\text{dim}(\mathcal{H})} |i \rangle |i \rangle$ is a maximally entangled state between the original system and
an ancilla.  Remarkably, the map $\mathcal{E}$
is completely positive if and only if $\mathcal{D}$ (also known as the Choi or
dynamical matrix of $\mathcal{E}$) is positive semidefinite.

@@

We have discussed the main features of quantum channels and 
now we turn our attention to a specific 
type of channel for $N$-qubit systems called Pauli channels.
First we define a Pauli channel on a one-qubit system,
whose most general single-qubit density
matrix can be written as
\begin{eqnarray}
\label{ec: Density Matrix}
\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
\end{eqnarray}
with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
The condition $\tr(\rho) = 1$ requires that $r_0 = 1$ while $\rho \geq 0$ 
implies that the remaining $r_{1,2,3}$ form
a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere. \cpnote{explicar un poco mejor. Me parece que para el publico vale 
la pena ser un poco mas explicito. pero no estoy muy seguro. }. 
A Pauli channel is defined as an operation that
applies each Pauli matrix $\sigma_{\gamma}$ to
the system with probabilities $k_{\gamma}$ with $\gamma = 0,1,2,3$. 
Mathematically, the Pauli channel is written in the following way:
\begin{eqnarray}
\label{ec: Pauli channel 1 qbit}
\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
\end{eqnarray} 
where of course the probabilities $k_{\gamma}$ of applying $\sigma_{\gamma}$
are non-negative real numbers such that 
$\sum_{\gamma} k_{\gamma} = 1$ (these conditions also ensure that the channel is 
trace preserving and completely positive). 
\cpnote{en todo hay que mejorar un poco la redaccion. Aca me gustaria que 
se interpretara. Creo qe es mas que atenuacion de los componentes, o es solo atenuacion? 
en todo caso ver mejor como va la cosa. }

Apart from this interpretation of Pauli channels,
we can find another one by seeing how the channel acts on the 
density matrix of eq. (\ref{ec: Density Matrix}).
To do it, we substitute eq. (\ref{ec: Density Matrix}) in eq. (\ref{ec: Pauli channel 1 qbit}):
\begin{equation}
\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
\end{equation}
This can be simplified by using the following property of Pauli matrices:
\begin{equation}
\label{ec: propiedad-pauli}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A_{\alpha,\gamma} = \begin{pmatrix}
1 & 1 & 1 & 1\\
1 & 1 & -1 &-1 \\
1 & -1 & 1 & -1 \\
1 & -1 & -1 & 1
\end{pmatrix},
\end{equation}
which leads to
\begin{equation}
\label{ec: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
Equation \ref{ec: rho-transformada} gives us another interpretation of Pauli channels.
Pauli channels take each component $r_{\alpha}$
of the density matrix and multiply them
by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
that is:
\begin{equation}
\label{ec: multipliers}
r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
\end{equation}
Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\gamma} A_{\gamma,\alpha} \tau_{\gamma}$.
Then, using that $k_{\gamma} \geq 0$ and $\sum_{\gamma} k_{\gamma} = 1$,
we get the following conditions on the multipliers:
\begin{eqnarray}
\label{eq: conditions-tetrahedron}
1+\tau_i -\tau_j - \tau_k \geq 0, \\
1+\tau_1 + \tau_2 + \tau_3 \geq 0.
\end{eqnarray}
These conditions imply that $(\tau_1,\tau_2,\tau_3)$
has to be inside a tetrahedron with
vertices $(1,1,1), (1,-1,-1),(-1,1,-1)$ and $(-1,-1,1)$. 
Therefore, the $\tau_{1,2,3}$ are numbers between 
$-1$ and $1$, which means that the components
$r_{\alpha}$ of the density matrix are always 
attenuated and possibly flipped sign.

Pauli channels can be used to model noise....

Having defined the one qubit case, 
in order to present the $N-$qubit one, we 
need to introduce the so-called \textit{Pauli strings}, defined as
\begin{eqnarray}
\label{ec: Pauli string}
\sigma_{\vec{\alpha}} = \sigma_{\alpha_1} \otimes \sigma_{\alpha_2}\otimes \cdots \otimes \sigma_{\alpha_N},
\end{eqnarray}
where $\vec{\alpha}$ denotes a multi-index $(\alpha_1, \cdots, \alpha_N)$
 and $\alpha_i \in \{0,1,2,3\}$. 
These operators form an orthogonal basis in the space of operators acting on $N$ qubits. 
 Similarly to the single-qubit case, the density matrix $\rho$ 
of a system of $N$ qubits can be written using Pauli strings as:
\begin{eqnarray}
\label{ec:  Density matrix Nqbit}
\rho = \dfrac{1}{2^N} \sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
\end{eqnarray}
Then, just as before we define a Pauli channel as a transformation that applies 
the operators $\sigma_{\vec{\gamma}}$ to $\rho$ with probabilities $k_{\vec{\gamma}}$
and is described mathematically by:
\begin{eqnarray}
\label{ec: pauli channel N-qubt}
\mathcal{E}(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}} \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
where just as before, complete positivity and trace preservation requires
that $k_{\vec{\gamma}}$ are non-negative real numbers such 
that $\sum_{\vec{\gamma}} k_{\vec{\gamma}}=1$.

\textbf{Interpretación de multiplicadores}

\cpnote{Creo qeu toca motivar, conectar con cosas conocidas y en general no ser tan seco}

% }}}
\subsection*{Pauli Dynamical Maps} % {{{
\label{subsec: Pauli Dynamical Maps}

% }}}
% }}}
\section{Circuit for a Pauli Channel} % {{{
\label{subsec: Circuit for a Pauli Channel}

@@

We are interested in constructing a quantum circuit that can implement an
arbitrary Pauli channel on a system of $N$ qubits. 
To do it, we remember that a Pauli channel as in eq.~(\ref{ec: pauli channel N-qubt})
is interpreted as a transformation that applies
each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.

Given this interpretation of the channel, 
it is easy to construct a quantum circuit that implements 
it with the help of $2n$ ancilla qubits.
The general idea is to create a state in the ancilla qubits that can then
be used to apply the operators $\sigma_{\vec{\gamma}}$
to the system.
The circuit that does this is presented in Fig~(\ref{fig: circuit-pauli}) and its 
first step in the circuit is to create the state
\begin{eqnarray}
\label{ec: state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
\end{eqnarray}
in the ancilla qubits, 
where $b_{\vec{\gamma}}$ is in general a complex number such that 
\begin{eqnarray}
\label{ec: b}
|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.
\end{eqnarray}
Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
\begin{eqnarray}
|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
\end{eqnarray}
where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\

@@

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1} }} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=7]{$|\vec{\gamma} \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & & & & & \\
\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS. Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel 
on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
on $2N$ ancilla qubits and then uses them to apply
all possible Pauli strings on the principal qubits
with probabilities $k_{\vec{\gamma}}$.}
\label{fig: circuit-pauli}
\end{figure}

@@

\subsection*{Simulation for one-qubit Pauli channels} % {{{
\label{subsec: Simulation for one-qubit Pauli channels}
For the particular case of a Pauli channel on one qubit, 
the circuit that simulates it can be constructed as in Fig~(\ref{fig: citcuit-pauli-1}),
 which is a special case of Fig(\ref{fig: circuit-pauli}).

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$aq_1$} & \gateinput{$b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{\tbnote{Al igual que antes, hay que adaptar esta figura y quitarla antes de entregar}. {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
\label{fig: citcuit-pauli-1} 
\end{figure}
Taking advantage of the quantum computers that IBM has available,
we sampled $250$ one-qubit Pauli channels and simulated them using the 
ibmq-lima quantum computer. 
For each of these channels, the accuracy of the implementation in the quantum computer
was quantified by calculating the
 process fidelity of the Choi matrix obtained by performing
quantum process tomography to the circuit
with respect to the theoretical Choi matrix of
the corresponding channel.
Finally, using the well known fact that one-qubit Pauli channels can be represented
as points in a tetrahedron with corners $(1,1,1), (1-1,-1), (-1,1,-1)$ and $(-1,-1,1)$, 
in Fig~(\ref{fig: fidelity one qubit}).
\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{fidelity-points.png}\\
\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}. {\bf Fidelities one-qubit Pauli channel} Fidelities of one-qubit Pauli channels implemented on IBM's ibmq-lima. The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the fidelity of each channel's implementation using the circuit for a 1-qubit Pauli channel}
\label{fig: fidelity one qubit}
\end{figure}

Dynamical maps can be implemented using the same circuit as 
in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
to be created on the ancilla qubits depends on parameter $p$ 
and therefore is given by 
\begin{eqnarray}
\label{ec: parametrized state}
\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
\end{eqnarray}
% }}}
% }}}

\section*{OPR Circuits} % {{{
\label{sec: OPR Circuits}
\textbf{Puntos:}
\begin{itemize}
\item As said before, to implement a Pauli dynamical map, 
we need to create the parametrized $2n$-qubit state 
$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
\item However, creating this state will in general require many rotations parametrized by $p$. 
For example, for the case of a Pauli dynamical map on 1 qubit, 
the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
In general, to create a parametrized state on $2n$ ancilla qubits will require
$2n-1$ rotations parametrized by $p$.
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{eqnarray}
U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
\end{eqnarray}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
aunque se puede y debe achicar bastante.
\end{itemize}
% }}}
\section*{OPR circuit for a Pauli map} % {{{
\label{sec: OPR circuit for a Pauli map}
\textbf{Puntos:}
\begin{itemize}
\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
Lo tengo para parabolic y para depolarizing.
\end{itemize}
% }}}
\section*{Exponential maps $e^{iHt}$} % {{{
\label{sec: Exponential maps}
\textbf{Puntos:}
